No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-19 main/LICS.tex
added main theorem

	\item
Otherwise, $\Delta=\Delta'$.
\end{enumerate}
\end{IEEEproof}

@@

>>>>

	\item
Otherwise, $\Delta=\Delta'$.
\end{enumerate}
\vskip-12pt
\end{IEEEproof}

@@

We are now ready to state our main theorem.

\begin{theorem}
MLL proof equivalence is \textsc{pspace}-complete.
\end{theorem}

\begin{IEEEproof}
MLL proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.
%
Then by Savitch's Theorem \cite{Savitch-1970} MLL proof equivalence is in \textsc{pspace}.

\textsc{pspace}-hardness follows by the encoding of \textsc{ncg}-reconfiguration, which in its completed form is stated:
\[
	\gamma\perm\delta \qquad\iff\qquad \itn\gamma\perm\itn\delta \text{ or } \itn\gamma\perm\itn\delta'~.
\]
%
The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\coitn{\itn\gamma'}=\gamma$.
%
\end{IEEEproof}
